In this paper, we study the evolution of communities through time. We show how by observing the behavior of the members of a community over a relatively short period of time (like one or two weeks), one can make predictions about its long-term growth. More specifically, we categorize members of each community into two groups: attractive and unattractive. Each person is categorized into one of these groups based on its success in attracting its friends into the community during a short period of time compared to the average performance of the members of that community. People whose performances are above the average are labeled as attractive members. Others are labeled as unattractive. We show how the size of these sets can be used for predicting the growth of communities. Those with larger percentages of attractive members are more probable to grow in the future. 

Note that since the performance of each person is only compared against the average,  the percentage of attractive members of a community is not an indicator of its growth rate, i.e. large growth rate does not mean large number of attractive members. A community can have a large growth rate over a time period, while having a small number of attractive members. This happens when there is a very small group of people in the community who have convinced a large number  of their friends to join the community while the others have attracted none or a very small number. As we will see, this type of growth implies a low chance for the growth of the community in the future. However, as we will show, unlike large growth rate, large fraction of attractive members can imply future growth of the community.


\subsection{Definitions} \label{sec: definitions}
\input{definitions}

\subsection{Observation} \label{sec: initial}
\input{initial_analysis}


\subsection{Regression analysis}\label{sec: regression}
\input{regression}

\subsection{Some further analysis}
\input{further}
