As mentioned before, in this paper we focus on LiveJournal which is an online social network with more than 19 million members.  It is an active social network with an average of 300,000 updates per day. 
Each member maintains a blog. They  declare friends, and join communities. Each community consists of a group of LJ members. The question is how each community evolves through time: does it grow, or freeze. 

The network, its members, and their connections can be well presented by a  friendship graph, whose nodes correspond to the users and its edges correspond to friendship relationships. To nodes are connected, it they are friends. Let the undirected graph $\mathcal{G}=(\mathcal{V},\mathcal{E})$ represent the friendship structure among the members of LiveJournal. Each node $v\in\mathcal{V}$ represents one of the members, and presence of each each edge $e=[v_1,v_2]\in\mathcal{E}$ shows that $v_1$ and $v_2$ are friends. 

There are different communities in LiveJournal. Each member can join as many communities as he/she desires. Hence, each community $\mathcal{C}$ corresponds to a subgroup of the members, and induces a subgraph $\mathcal{G}_{\mathcal{C}}=[\mathcal{C},\mathcal{E}_{\mathcal{C}}]$ of the main graph $\mathcal{G}$ such that  each edge $e=[v_1,v_2]\in\mathcal{E}$ with $v_1\in\mathcal{C}$ and  $v_2\in\mathcal{C}$ belongs to $\mathcal{G}_{\mathcal{C}}$ as well.

For this study, we followed the evolution of more than $2000$ communities, and collected data over seven snapshots during a period of five months.  The time intervals between the snapshots is shown in Table \ref{tb:data}. At each snapshot, we recorded the  members of each of the 2000 communities. Moreover, for each  member, we registered his/her friends, both inside and outside the community. 

\begin{table}[htdp]
\begin{center}
\begin{tabular}{|c|c|}
\hline
Snapshot  & Time between the snapshot  \\
  & and its previous one \\ \hline
0 & -  \\ \hline
1 & 1 week \\ \hline
2 & 1 week \\ \hline
3 & 1 week \\ \hline
4 & 2 weeks \\ \hline
5 & 8 weeks \\ \hline
6 & 6 weeks \\ \hline
\end{tabular}
\end{center}\caption{Brief description of the data}
\label{tb:data}
\end{table}%

